### 2015-12-30 fundamentals/examples.tex
figure and table adjustments for final submission
reduces length of qa section at request of reviewer 2
Adds references to previous benchmarking work

\begin{table}[H]
\centering
\begin{tabularx}{\columnwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table*}[H]
\centering
\begin{tabularx}{\columnwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table*}

@@

To illustrate the flexibility of \Cyclus, this section will discuss the 
creation and results of a range of representative fuel cycle simulations.
These examples are not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus matches the capabilities of any
recipe-based simulator and that variations on a single \Cyclus simulations can 
be run with small changes to the input specification. For simplicity of the 
demonstration, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:

@@

\begin{table*}[H]
\centering
\begin{tabularx}{\columnwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20$ [MTHM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Spent Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table*}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/puseries-n.eps}
\end{center}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\label{fig:puseriesn}
\end{figure}

>>>>

\begin{table*}[htb]
\centering
\begin{tabularx}{\textwidth}{rXr}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Ref.} \\
\hline
Cycic &  Input control embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table*}

@@

\begin{table*}[htb]
\centering
\begin{tabularx}{\textwidth}{rXr}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Ref.} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table*}

@@

To illustrate the flexibility of \Cyclus, this section will discuss the 
creation and results of a range of representative fuel cycle simulations.
Previous benchmarks between 
\Cyclus and system dynamics simulators for more complex problems, including 
transition analyses, have been reported 
elsewhere and \Cyclus has demonstrated satisfactory performance
\cite{djokic_application_2015,scopatz_non-judgemental_2015,gidden_once-through_2012} . 
The current examples are not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus matches the capabilities of any
recipe-based simulator and that variations on a single \Cyclus simulations can 
be run with small changes to the input specification. 
For simplicity of the current demonstration, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:

@@

\begin{table*}[htb]
\centering
\begin{tabularx}{\textwidth}{XrX}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20$ [MTHM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Spent Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table*}
\twocolumn

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\columnwidth]{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\columnwidth]{./images/puseries-n.eps}
\end{center}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\label{fig:puseriesn}
\end{figure}
